Bayesian analysis of the NESTA study of interventions against  verbal aggression online \\linebreak  Technical Report

### 2023-12-18 technical_report/nesta_study_technical_report.Rmd

```{r periodsVisualisationPrep,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE, tidy = FALSE}
Hate <- readRDS(file = "datasets/RAWNESTA/Hate.rds")
Comments <-   readRDS(file = "datasets/RAWNESTA/Comments.rds")
summaries <- read.csv(file = "datasets/Summaries.csv")

@@

interventions <- readRDS(file = "datasets/interventions.rds")
interventionsTS <- as.data.frame(table(interventions$day))
interventionsTS$Var1 <- as.Date(interventionsTS$Var1)
colnames(interventionsTS) <- c("date", "interventions")

@@

\vspace{1mm}
\footnotesize
```{r tsVisPrep,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE}
hateDFs <- readRDS("datasets/hateDFsNoDropouts.RDS")

@@

\footnotesize
```{r nullTSmodels,echo=TRUE,eval=FALSE,fig.align = "center", cache=TRUE, fig.show = "hold", out.width = "100%",   message = FALSE, warning = FALSE, results = FALSE}
dat <- readRDS(file = "datasets/dat.RDS")

@@

#prior predictive checks sd =1
ADS <- 0
CBS <- 0
groupID <- 1:3
IC <- 5  #mean for interventions in treatment
data <- expand.grid(ADS = ADS,groupID = groupID, CBS = CBS, IC =  IC)
#prior <- extract.prior(InteractionsModelDiffSD1, n = 1e4)
#saveRDS(prior, file = "datasets/prior1.RDS")
prior <- readRDS(file = "datasets/prior1.RDS")
mu <- link( InteractionsModelDiffSD1 , post=prior , data=data )
colnames(mu) <- levels(summaries$group)
muLong <- melt(mu)
colnames(muLong) <- c("id", "group", "AdiffS")

@@

ADS <- 0
CBS <- 0
groupID <- 1:3
IC <- 0:20
data <- expand.grid(ADS = ADS,groupID = groupID, CBS = CBS, IC =  IC)
#prior <- extract.prior(InteractionsModelDiffSD1, n = 1e4)
#saveRDS(prior, file = "datasets/prior2.RDS")
prior <- readRDS(file = "datasets/prior2.RDS")
mu <- link(InteractionsModelDiffSD1 , post=prior , data=data )
mu.mean <- apply( mu , 2, mean )
mu.HPDI <- data.frame(t(apply( mu , 2 , HPDI )))
priorDF <- cbind(data, mu.mean, mu.HPDI)
priorDF$groupID <- as.factor(groupID)
levels(priorDF$groupID) <- c("control", "empathy", "normative")
colnames(priorDF)[2]<- "group"

@@

#Some experimentation leads to the value of $\sigma =.3$, which leads to the following priors:
#prior predictive check sd =.3
ADS <- 0
CBS <- 0
groupID <- 1:3
IC <- 5  #mean for interventions in treatment
data <- expand.grid(ADS = ADS,groupID = groupID, CBS = CBS, IC =  IC)
#prior <- extract.prior(InteractionsModelDiff, n = 1e4)
#saveRDS(prior, file = "datasets/prior3.RDS")
prior <- readRDS(file = "datasets/prior3.RDS")

@@

ADS <- 0
CBS <- 0
groupID <- 1:3
IC <- 0:20
data <- expand.grid(ADS = ADS,groupID = groupID, CBS = CBS, IC =  IC)
#prior <- extract.prior(InteractionsModelDiff, n = 1e4)
#saveRDS(prior, file = "datasets/prior4.RDS")
prior <- readRDS(file = "datasets/prior4.RDS")
mu <- link(InteractionsModelDiff , post=prior , data=data )
mu.mean <- apply( mu , 2, mean )
mu.HPDI <- data.frame(t(apply( mu , 2 , HPDI )))
priorDF <- cbind(data, mu.mean, mu.HPDI)
priorDF$groupID <- as.factor(groupID)
levels(priorDF$groupID) <- c("control", "empathy", "normative")
colnames(priorDF)[2]<- "group"

@@

\begin{figure}
```{r traceplot,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "80%", results = "hide"}
InteractionsModelDiff <- readRDS(file = "models/InteractionsModelDiff.rds")
traceplot( InteractionsModelDiff )
```
\caption{Traceplot of the model selected using Widelly Acceptable Information Criterion.}
\label{fig:traceplot}
\end{figure}

@@

hateDFs <- readRDS(file ="datasets/hateDFs2.RDS")
sampleDFs <- hateDFs

d1precis <- readRDS("timeSeriesDFs/d1precis.rds")
d2precis <- readRDS("timeSeriesDFs/d2precis.rds")
d3precis <- readRDS("timeSeriesDFs/d3precis.rds")
d4precis <- readRDS("timeSeriesDFs/d4precis.rds")
d5precis <- readRDS("timeSeriesDFs/d5precis.rds")
d6precis <- readRDS("timeSeriesDFs/d6precis.rds")
d7precis <- readRDS("timeSeriesDFs/d7precis.rds")

@@

datA <- readRDS(file = "timeSeries/tsaStanCumulative/datA.RDS")
fitA <- readRDS("timeSeries/tsaStanCumulative/c3interactionStanFitA.rds")
datB <- readRDS(file = "timeSeries/tsaStanCumulative/datB.RDS")
fitB <- readRDS("timeSeries/tsaStanCumulative/c3interactionStanFitB.rds")
datC <- readRDS(file = "timeSeries/tsaStanCumulative/datC.RDS")
fitC <- readRDS("timeSeries/tsaStanCumulative/c3interactionStanFitC.rds")
datD <- readRDS(file = "timeSeries/tsaStanCumulative/datD.RDS")
fitD <- readRDS("timeSeries/tsaStanCumulative/c3interactionStanFitD.rds")

>>>>

```{r periodsVisualisationPrep,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE, tidy = FALSE}
Hate <- readRDS(file = "data/raw/Hate.rds")
Comments <-   readRDS(file = "data/raw/Comments.rds")
summaries <- read.csv(file = "data/Summaries.csv")

@@

interventions <- readRDS(file = "data/interventions.rds")
interventionsTS <- as.data.frame(table(interventions$day))
interventionsTS$Var1 <- as.Date(interventionsTS$Var1)
colnames(interventionsTS) <- c("date", "interventions")

@@

\vspace{1mm}
\footnotesize
```{r tsVisPrep,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE}
hateDFs <- readRDS("data/hateDFsNoDropouts.RDS")

@@

\footnotesize
```{r nullTSmodels,echo=TRUE,eval=FALSE,fig.align = "center", cache=TRUE, fig.show = "hold", out.width = "100%",   message = FALSE, warning = FALSE, results = FALSE}
dat <- readRDS(file = "data/dat.RDS")

@@

#prior predictive checks sd =1
ADS <- 0
CBS <- 0
groupID <- 1:3
IC <- 5  #mean for interventions in treatment
data <- expand.grid(ADS = ADS,groupID = groupID, CBS = CBS, IC =  IC)
#prior <- extract.prior(InteractionsModelDiffSD1, n = 1e4)
#saveRDS(prior, file = "data/prior1.RDS")
prior <- readRDS(file = "data/prior1.RDS")
mu <- link( InteractionsModelDiffSD1 , post=prior , data=data )
colnames(mu) <- levels(summaries$group)
muLong <- melt(mu)
colnames(muLong) <- c("id", "group", "AdiffS")

@@

ADS <- 0
CBS <- 0
groupID <- 1:3
IC <- 0:20
data <- expand.grid(ADS = ADS,groupID = groupID, CBS = CBS, IC =  IC)
#prior <- extract.prior(InteractionsModelDiffSD1, n = 1e4)
#saveRDS(prior, file = "data/prior2.RDS")
prior <- readRDS(file = "data/prior2.RDS")
mu <- link(InteractionsModelDiffSD1 , post=prior , data=data )
mu.mean <- apply( mu , 2, mean )
mu.HPDI <- data.frame(t(apply( mu , 2 , HPDI )))
priorDF <- cbind(data, mu.mean, mu.HPDI)
priorDF$groupID <- as.factor(groupID)
levels(priorDF$groupID) <- c("control", "empathy", "normative")
colnames(priorDF)[2]<- "group"

@@

#Some experimentation leads to the value of $\sigma =.3$, which leads to the following priors:
#prior predictive check sd =.3
ADS <- 0
CBS <- 0
groupID <- 1:3
IC <- 5  #mean for interventions in treatment
data <- expand.grid(ADS = ADS,groupID = groupID, CBS = CBS, IC =  IC)
#prior <- extract.prior(InteractionsModelDiff, n = 1e4)
#saveRDS(prior, file = "data/prior3.RDS")
prior <- readRDS(file = "data/prior3.RDS")

@@

ADS <- 0
CBS <- 0
groupID <- 1:3
IC <- 0:20
data <- expand.grid(ADS = ADS,groupID = groupID, CBS = CBS, IC =  IC)
#prior <- extract.prior(InteractionsModelDiff, n = 1e4)
#saveRDS(prior, file = "data/prior4.RDS")
prior <- readRDS(file = "data/prior4.RDS")
mu <- link(InteractionsModelDiff , post=prior , data=data )
mu.mean <- apply( mu , 2, mean )
mu.HPDI <- data.frame(t(apply( mu , 2 , HPDI )))
priorDF <- cbind(data, mu.mean, mu.HPDI)
priorDF$groupID <- as.factor(groupID)
levels(priorDF$groupID) <- c("control", "empathy", "normative")
colnames(priorDF)[2]<- "group"

@@

<!-- ```{r traceplot,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "80%", results = "hide"} -->
<!-- InteractionsModelDiff <- readRDS(file = "models/InteractionsModelDiff.rds") -->
<!-- traceplot( InteractionsModelDiff ) -->
<!-- ``` -->
<!-- \caption{Traceplot of the model selected using Widelly Acceptable Information Criterion.} -->
<!-- \label{fig:traceplot} -->
<!-- \end{figure} -->

@@

hateDFs <- readRDS(file ="data/hateDFs2.RDS")
sampleDFs <- hateDFs

d1precis <- readRDS("data/timeSeriesDFs/d1precis.rds")
d2precis <- readRDS("data/timeSeriesDFs/d2precis.rds")
d3precis <- readRDS("data/timeSeriesDFs/d3precis.rds")
d4precis <- readRDS("data/timeSeriesDFs/d4precis.rds")
d5precis <- readRDS("data/timeSeriesDFs/d5precis.rds")
d6precis <- readRDS("data/timeSeriesDFs/d6precis.rds")
d7precis <- readRDS("data/timeSeriesDFs/d7precis.rds")

@@

datA <- readRDS(file = "data/timeSeries/datA.RDS")
fitA <- readRDS("data/timeSeries/c3interactionStanFitA.rds")
datB <- readRDS(file = "data/timeSeries/datB.RDS")
fitB <- readRDS("data/timeSeries/c3interactionStanFitB.rds")
datC <- readRDS(file = "data/timeSeries/datC.RDS")
fitC <- readRDS("data/timeSeries/c3interactionStanFitC.rds")
datD <- readRDS(file = "data/timeSeries/datD.RDS")
fitD <- readRDS("data/timeSeries/c3interactionStanFitD.rds")
